Parsing Tweets into Universal Dependencies

### 2017-09-25 paper.tex
sync.

Universal dependencies \citep[UD]{NIVRE16.348} was created to delivery
consistent annotation across different languages. To allow such
consistency, UD was designed to be adaptive to different genres and languages
\cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. It's promising that analyzing
the syntax of tweets can benefit from such adaptability. In this paper,
we create a new tweets treebank of 55,607 tokens by following the UD
guidelines but also contending the domain-specific challenges which wasn't
covered by UD guidelines. Our annotation includes a whole pipeline of
tokenization, part-of-speech (POS) tags and universal dependencies.

@@

We adopt UD version 2 
\cite{Marneffe2014UniversalSD} guidelines to annotate the syntax of tweets.
In applying UD annotation conventions to tweets, the choices of 
\newcite{kong-EtAl:2014:EMNLP2014} must be revisited.  We consider the
key questions that arose in our annotation effort, and how we resolved them.

@@

\paragraph{Acronym abbreviations.}  How should we syntactically
analyze acronym tokens like \emph{mfw}
(abbreviating ``my face when'') and \emph{rn} (``right now'')?  Should
they be decomposed into their component words, and if so should those
words be ``normalized'' into explicitly spelled out intermediate
forms?  \nascomment{explain what we do, and include how this is
  similar to or different from Kong et al}

\nascomment{maybe we owe citations to
  \cite{finin-EtAl:2010:MTURK,eisenstein:2013:NAACL-HLT} here?  maybe
  better papers to cite}

\paragraph{Non-syntactic tokens.}  
Figure \ref{fig:non-syn-toks} illustrates examples of tokens that have
no syntactic function.  Note that these generally have the
\emph{other} (\texttt{X}) part of speech.

It is important to note that these types may, in some
contexts, have syntactic functions.
For example, besides being a discourse marker, \emph{RT} can
abbreviate the verb {\tt retweet}, and emoticons and hashtags may be
used as content words within a sentence; see  Figure
\ref{fig:informal-toks}.  Therefore, the criteria for annotating a
token as non-syntactic must be context-dependent.
To our knowledge, this issue has not previously been addressed in UD
annotation efforts \nascomment{check!}.

\nascomment{I'm confused about (1) how we define non-syntactic tokens
  (what are the criteria) and (2) whether this is something we kick
  over to POS annotation}

@@

\nascomment{explain our conventions and how
  they relate to Kong and to UD.  in the draft before, we said that we
had conventions, and Kong didn't, but we didn't really say what ours were.}

@@

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& @coldplay \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl}\\
			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny X \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \\
		\end{deptext}
		\deproot{1}{root}
		\depedge[edge unit distance=1em]{1}{2}{discourse}
		\deproot{6}{root}
		\depedge[edge unit distance=1em]{6}{3}{discourse}
		\depedge[edge unit distance=1em]{3}{4}{discourse}
		\depedge[edge unit distance=1em]{3}{5}{punct}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.8em]{6}{10}{obl}
		\depedge[edge unit distance=1em]{10}{8}{case}
		\depedge[edge unit distance=1em]{10}{9}{det}
		\depedge[edge unit distance=0.8em]{6}{11}{discourse}
		\depedge[edge unit distance=0.8em]{6}{12}{list}
	\end{dependency}
	\caption{A example tweet contains major non-syntactic tokens, with
		\textcolor{red}{sentiment emoticon},
		\textcolor{orange}{retweet marker},
		\textcolor{gray}{topical hashtag}, and
		\textcolor{blue}{referential URL}.}\label{fig:non-syn-toks}
\end{figure*}

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			its \& \#awesome \& u \& gonna \& $\heart$ \& it \& Chk \& out \& our \& cooool \& project \& on \& http:// \& + \& RT \& pls\\
			\tiny PRON \& \tiny ADJ \& \tiny PRON \& \tiny VERB \& \tiny VERB \& \tiny PRON \& \tiny VERB \& \tiny ADP \& \tiny PRON \& \tiny ADJ \& \tiny NOUN \& \tiny ADP \& \tiny X \& \tiny SYM \& \tiny VERB\& \tiny INTJ\\
		\end{deptext}
		\deproot{2}{root}
		\depedge[edge unit distance=1em]{2}{1}{nsubj}
		\depedge[edge unit distance=1em]{2}{4}{parataxis}
		\depedge[edge unit distance=1em]{4}{3}{nsubj}
		\depedge[edge unit distance=1em]{4}{5}{xcomp}
		\depedge[edge unit distance=1em]{5}{6}{obj}
		\depedge[edge unit distance=0.7em]{2}{7}{parataxis}
		\depedge[edge unit distance=1em]{7}{8}{compound:prt}
		\depedge[edge unit distance=0.7em]{7}{11}{obj}
		\depedge[edge unit distance=1em]{11}{9}{nmod:poss}
		\depedge[edge unit distance=1em]{11}{10}{amod}
		\depedge[edge unit distance=1em]{11}{13}{nmod}
		\depedge[edge unit distance=1em]{13}{12}{case}
		\depedge[edge unit distance=0.45em]{7}{15}{conj}
		\depedge[edge unit distance=1em]{15}{14}{cc}
		\depedge[edge unit distance=0.35em]{2}{16}{discourse}
	\end{dependency}
	\caption{An example tweet with informal but syntactic tokens.}\label{fig:informal-toks}
\end{figure*}

@@

\nascomment{in latex source I've commented out a paragraph about
  truncated content.  it's not clear to me what the nonsyntactic
  tokens are, when that happens}
% A kind of token that doesn't carry clearly syntactic functions can be resulted by the 140 characters limits of tweets.
% Since last tokens that exceeding 140 characters limits are truncated in tweets which leaves a broken sentence, it is impossible to fully recover their original form and figure out their syntactics.
% In this paper, we propose to treat these truncated tokens, along with the other 4 kinds of tokens mentioned above, as ones without syntactic functions.

\newcite{kong-EtAl:2014:EMNLP2014} proposed an additional
preprocessing step, \emph{token selection}, to remove non-syntactic
tokens before parsing.  \nascomment{confusing.  were they removed or
  just labeled as non-syntactic and then excluded from the tree?  I
  think they were not actually removed, and were still available,
  e.g., for defining features of the input for parsing}  In order to
keep our annotation conventions in line with UD norms, we include
non-syntactic tokens in the dependency analysis, with a special label
\nascomment{say what it is, and what they attach to, and clarify that
  the annotators didn't do this manually (I think)}

@@

\paragraph{Vocative at-mentions.}  Another idiomatic construction on
Twitter is an at-mention (followed by a colon \nascomment{?}) as a
sign that a tweet is a reply to a tweet by the mentioned user.  We
treat these at-mentions as vocative expressions, labeling them as
\emph{proper noun} (\texttt{PROPN}) and attaching them to the
following predicate with the label \emph{vocative}.  \nascomment{need an example.}

@@

\nascomment{I didn't touch anything below here}

@@

\subsubsection{Annotation Process}
The whole annotation process contains their stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1} proportion and created the initial annotation in one day.
This annotation was further refined by the authors of this paper to solve inconsistency between different annotators.
In the second stage, a postagger and parser are trained on the annotated data from the first stage, and automatically analyze the sampled 2,500 tweets and the authors of this paper manually correct these automatically annotated.
Finally, an extra layer of word-level normalization was manually annotated.

We report the inter-annotator agreement between the annotators in the second stage.
The agreement on POS is 95.16\%, the unlabeled dependency agreement is 88.43\% and the labeled dependency agreement is 83.89\%.
Further analysis shows the major disagreement on POS happens.

\subsubsection{Statistics}
\yjcomment{this part is not finished}
Tweebank V2 contains 3550 tweets in total, split into training set with 1639 tweets, development set with 710 tweets and test set with 1201 tweets. 
The training set contains all the 639 unique tweets in the training set of Tweebank V1 and another 1000 tweets in feb\_jul\_16 corpus.
The development set contains 210 tweets of Tweebank V1 Dev and another 500 tweets in feb\_jul\_16 corpus.
The test set contains all the 201 tweets in the test set of Tweebank V1 and another 1000 tweets in feb\_jul\_16 corpus.

We process all the raw tweets of these corpora from scratch, from tokenization and POS tagging to dependency annotation.
As Tweebank V1 and the POS-tagged Twitter corpus of \newcite{gimpel-EtAl:2011:ACL-HLT2011} used a tweet tokenizer~\cite{ICWSM101540} that do not conform with UD guidelines, as we discussed before, we did not use any data of the intermediate steps from these corpora. The basic statistics of Tweebank V2 is shown in Table~\ref{tab1}.

% tweets, tokens, tokens/tweet, part/tweet, token types.
\begin{table}[t]
	\centering
	\begin{tabular}{l r r r} 
		\hline
		& 	Train 		& 	Dev		&	Test\\[0.5ex] \hline
		tweets 		&	1,639 		&	709		&	1,201\\
		tokens 		&	24,753		&	11,742	&	19,112\\
		types 		&	7,579			&	4,165		&	6,228\\
		parts		 	&	3,025 		&	1,402		&	2,252\\ \hline
	\end{tabular}
	\caption{Basic Statistics of Tweebank V2}
	\label{tab1}
\end{table}

% tokens and its proportions for the previous language phenomena.
\subsubsection{Twitter Specific Statistics}\label{stats}
Following the discussion of the Twitter specific linguistic phenomena, we obtain Table~\ref{tab2}.

\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{r | l | l | l | r r r r r} 
		\hline
		\multicolumn{4}{l}{}	&	Train		&	Test	&	Dev	&	All	&	Per\\[0.5ex] \hline\hline
		\multirow{10}{*}{\textit{token}}	&	syntactic						&	\multicolumn{2}{l |}{phrasal abbreviation}				
		&	 12 		&	12	&	10	&	34	&	0.06\%	\\
		\cline{2-9}
		&	\multirow{8}{*}{optionally syntactic}	&	\multirow{2}{*}{RT}					&	syntactic	
		&	 40 		&	19	&	18	&	77	&	0.14\%	\\
		&								&									&	non-syntactic
		&	600  		&	500	&	286	&	1386	&	2.49\%	\\
		\cline{3-9}
		&								&	\multirow{2}{*}{hashtag}				&	syntactic
		&	251  		&	212	&	103	&	566	&	1.02 \%	\\
		&								&									&	non-syntactic
		&	 290 		&	246	&	155	&	691	&	1.24\%	\\
		\cline{3-9}
		&								&	\multirow{2}{*}{at-mentioned}			&	syntactic
		&	  659		&	420	&	257	&	1336	&	2.40\%	\\
		&								&									&	non-syntactic
		&	  640		&	519	&	311	&	1470	&	2.64\%	\\
		\cline{3-9}
		&								&	\multirow{2}{*}{emoticon/emoji}			&	syntactic
		&	  59		&	31	&	24	&	114	&	2.05\%	\\
		&								&									&	non-syntactic
		&	 233		&	164	&	98	&	495	&	0.89\%	\\
		\cline{2-9}
		&	non-syntactic 					&	\multicolumn{2}{l |}{truncated}
		&	  111		&	110	&	50	&	271	&	0.49\%	\\

		\hline
		\multirow{3}{*}{\textit{structure}}	& 	\multicolumn{3}{l |}{retweet}
		&	  596		&	498	&	282	&	1376	&	2.47\%	\\
		&	\multicolumn{3}{l |}{at-mentioned}
		&	  485		&	305	&	175	&	965	&	1.74\%	\\
		\hline
	\end{tabular}
	\caption{Twitter Specific Statistics of Tweebank V2}
	\label{tab2}
\end{table*}

@@

We present a pipeline model to parse tweets into universal dependency.

\subsection{Tokenizer}
Tokenization is non-trivial for Twitter domain \cite{ICWSM101540}.
Due to the informal nature, tweets present cases which are unconventional for traditional toeknization module, like hashtags, at-mentions and emoticons.
Some of them are even ambiguous without understanding their contexts.
For example, the asterisk in {\it 4*3} works as a symbol for times and indicates to segment this token into {\it 4 * 3} but that in {\it SH*T} works as a mask and {\it SH*T} should not be segmented.

Instead of manually crafting rules, we propose to deal with tweets tokenization with a character-level bidirectional LSTM (bi-LSTM) sequence-labeling model.
Our model takes the raw sentence and tag each character in this sentence as whether it is the beginning of a word.

>>>>

Universal dependencies \citep[UD]{NIVRE16.348} was created to deliver
consistent annotation across different languages. To allow such
consistency, UD was designed to be adaptive to different genres and languages
\cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. It's promising that analyzing
the syntax of tweets can benefit from such adaptability. In this paper,
we create a new tweets treebank of 55,607 tokens by following the UD
guidelines but also contending the domain-specific challenges which wasn't
covered by UD guidelines. Our annotation includes a whole pipeline of
tokenization, part-of-speech (POS) tags and universal dependencies.

@@

We adopt UD version 2 guidelines to annotate the syntax of tweets.
In applying UD annotation conventions to tweets, the choices of 
\newcite{kong-EtAl:2014:EMNLP2014} must be revisited.  We consider the
key questions that arose in our annotation effort, and how we resolved them.

@@

\paragraph{Acronym abbreviations.}  How should we syntactically
analyze acronym tokens like \emph{idc}
(abbreviating ``I don't care'') and \emph{rn} (``right now'')?  Should
they be decomposed into their component words, and if so should those
words be ``normalized'' into explicitly spelled out intermediate
forms? We follow \citet{kong-EtAl:2014:EMNLP2014} and annotate their
syntax as a single word without normalization. Their syntactic functions
are decided according to their context.
\nascomment{explain what we do, and include how this is
	similar to or different from Kong et al}\yjcomment{done.}

\citet{eisenstein:2013:NAACL-HLT} studied the necessity of normalization
in social media text and pointed that such normalization is problematic.
Our solution to the syntax of abbreviations is in the same spirit with
his work. Further study shows that the abbreviations which clearly carry
syntactic functions only make 0.06\% tokens in our dataset, which
also indicates it's unnecessary to normalize text in social media.
\nascomment{maybe we owe citations to
  \cite{finin-EtAl:2010:MTURK,eisenstein:2013:NAACL-HLT} here?  maybe
  better papers to cite}

\paragraph{Non-syntactic tokens.}  
\begin{table}
\centering
\small
\begin{tabular}{rcc}
\% & syntactic & non-syntactic \\ \hline
emoticons & 0.25 & 0.95 \\
RT & 0.14 & 2.49\\
hashtag & 1.02 & 1.24 \\
URL & 0.67 & 2.38 \\
truncated words & 0 & 0.49 \\
 \hline
 sum & 2.08 & 7.55 \\
\end{tabular}
\caption{Proportion of non-syntactic tokens in the annotation.}\label{tbl:non-synt-prop}
\end{table}
The major characteristic that distinguishes tweets from standard texts is that
there are large proportion of tokens that don't carry any syntactic functions.
In our annotation, there are five types of non-syntactic tokens which include
sentiment emoticons, retweet markers, topical hashtags, referential URLs, and
truncated words. Figure \ref{fig:non-syn-toks} illustrates examples of
these non-syntactic tokens. In the sense of part of speech, emoticons are tagged
as \emph{symbol} ({\tt SYM}) by following the UD guidelines. For other 4 types of
non-syntactic tokens, they generally have the \emph{other} (\texttt{X})
part of speech. In our annotation, these five types of tokens make more than
7.5\% of all tokens and detailed statistics can be found in Table \ref{tbl:non-synt-prop}.
\nascomment{in latex source I've commented out a paragraph about
	truncated content.  it's not clear to me what the nonsyntactic
	tokens are, when that happens}\yjcomment{i've put truncated words here.}

It is important to note that these types may, in some
contexts, have syntactic functions.
For example, besides being a discourse marker, \emph{RT} can
abbreviate the verb {\tt retweet}, and emoticons and hashtags may be
used as content words within a sentence; see  Figure
\ref{fig:informal-toks}.  Therefore, the criteria for annotating a
token as non-syntactic must be context-dependent.
%To our knowledge, this issue has not previously been addressed in UD
%annotation efforts \nascomment{check!}\yjcomment{it's not safe to claim that.}.

\nascomment{I'm confused about (1) how we define non-syntactic tokens
  (what are the criteria) and (2) whether this is something we kick
  over to POS annotation}
\yjcomment{I've put the definition of non-syntactic tokens there.}

@@

\nascomment{explain our conventions and how
  they relate to Kong and to UD.  in the draft before, we said that we
had conventions, and Kong didn't, but we didn't really say what ours were.}
\yjcomment{The bullet points describe our convention for non-syntactic tokens.}

@@

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& @coldplay \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl} \& Nice \& \textcolor{cyan}{\bf p} \& ...\\
			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny X \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \& \tiny ADJ \& \tiny X \& \tiny PUNCT \\
		\end{deptext}
		\deproot{1}{root}
		\depedge[edge unit distance=1em]{1}{2}{discourse}
		\deproot{6}{root}
		\depedge[edge unit distance=1em]{6}{3}{discourse}
		\depedge[edge unit distance=1em]{3}{4}{discourse}
		\depedge[edge unit distance=1em]{3}{5}{punct}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.8em]{6}{10}{obl}
		\depedge[edge unit distance=1em]{10}{8}{case}
		\depedge[edge unit distance=1em]{10}{9}{det}
		\depedge[edge unit distance=0.8em]{6}{11}{discourse}
		\depedge[edge unit distance=0.8em]{6}{12}{list}
		\deproot{13}{root}		
		\depedge[edge unit distance=0.8em]{13}{14}{discourse}
		\depedge[edge unit distance=0.8em]{13}{15}{punct}
	\end{dependency}
	\caption{A example tweet contains major non-syntactic tokens, with
		\textcolor{red}{sentiment emoticon},
		\textcolor{orange}{retweet marker},
		\textcolor{gray}{topical hashtag},
		\textcolor{blue}{referential URL}, and
		\textcolor{cyan}{truncated word}.}\label{fig:non-syn-toks}
\end{figure*}

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			@username \& its \& \#awesome \& u \& gonna \& $\heart$ \& it \& Chk \& out \& our \& cooool \& project \& on \& http:// \& + \& RT \& pls\\
			\tiny PROPN \& \tiny PRON \& \tiny ADJ \& \tiny PRON \& \tiny VERB \& \tiny VERB \& \tiny PRON \& \tiny VERB \& \tiny ADP \& \tiny PRON \& \tiny ADJ \& \tiny NOUN \& \tiny ADP \& \tiny X \& \tiny SYM \& \tiny VERB\& \tiny INTJ\\
		\end{deptext}
		\deproot{3}{root}
		\depedge[edge unit distance=1em]{3}{1}{vocative}
		\depedge[edge unit distance=1em]{3}{2}{nsubj}
		\depedge[edge unit distance=1em]{3}{5}{parataxis}
		\depedge[edge unit distance=1em]{5}{4}{nsubj}
		\depedge[edge unit distance=1em]{5}{6}{xcomp}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.7em]{3}{8}{parataxis}
		\depedge[edge unit distance=1em]{8}{9}{compound:prt}
		\depedge[edge unit distance=0.7em]{8}{12}{obj}
		\depedge[edge unit distance=1em]{12}{10}{nmod:poss}
		\depedge[edge unit distance=1em]{12}{11}{amod}
		\depedge[edge unit distance=1em]{12}{14}{nmod}
		\depedge[edge unit distance=1em]{14}{13}{case}
		\depedge[edge unit distance=0.45em]{8}{16}{conj}
		\depedge[edge unit distance=1em]{16}{15}{cc}
		\depedge[edge unit distance=0.35em]{3}{17}{discourse}
	\end{dependency}
	\caption{An example tweet with informal but syntactic tokens.}\label{fig:informal-toks}
\end{figure*}

@@

% A kind of token that doesn't carry clearly syntactic functions can be resulted by the 140 characters limits of tweets.
% Since last tokens that exceeding 140 characters limits are truncated in tweets which leaves a broken sentence, it is impossible to fully recover their original form and figure out their syntactics.
% In this paper, we propose to treat these truncated tokens, along with the other 4 kinds of tokens mentioned above, as ones without syntactic functions.

\newcite{kong-EtAl:2014:EMNLP2014} proposed an additional
preprocessing step, \emph{token selection}, in their annotation process.
They required the annotators to first select the non-syntactic
tokens and exclude them from the final dependencies annotation.
%  \nascomment{confusing.  were they removed or
%  just labeled as non-syntactic and then excluded from the tree?  I
%  think they were not actually removed, and were still available,
%  e.g., for defining features of the input for parsing}
In order to keep our annotation conventions in line with UD norms,
we include non-syntactic tokens in our annotation following the
convention above. Compared with \citet{kong-EtAl:2014:EMNLP2014},
we also gave a clear definition of non-syntactic tokens, which help
us avoid confusion.
\nascomment{say what it is, and what they attach to, and clarify that
  the annotators didn't do this manually (I think)}

@@

\paragraph{Vocative at-mentions.}  Another idiomatic construction on
Twitter is an at-mention %(followed by a colon \nascomment{?})
as a sign that a tweet is a reply to a tweet by the mentioned user.  We
treat these at-mentions as vocative expressions, labeling them as
\emph{proper noun} (\texttt{PROPN}) and attaching them to the
following predicate with the label \emph{vocative} (see Figure \ref{fig:informal-toks} for an example).  \nascomment{need an example.} \yjcomment{done.}

@@

%\nascomment{I didn't touch anything below here}

@@

\subsubsection{Annotation Process}
The whole annotation process contains three stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1}
proportion and created the initial annotation in one day
following our guideline. Both the guideline and annotation
were further refined by the authors of this paper to increase
the coverage of our guideline and solve inconsistency between
different annotators. In the second stage, a postagger and
parser are trained on the annotated data from the first stage,
and automatically analyze the sampled 2,500 tweets and the authors
of this paper manually correct the parsed data. Finally, an extra
layer of word-level normalization was manually annotated.

\begin{figure}
\centering
\small
\begin{dependency}[edge slant=2, text only label, label style=above]
	\begin{deptext}
		Olympic \& gold \& medallist \& whipped \& by \& John \& Fisher \\
	\end{deptext}
	\deproot{3}{root}
	\depedge[edge unit distance=1em]{3}{1}{amod}
    \depedge[edge unit distance=1em]{3}{2}{compound}
    \depedge[edge unit distance=1em]{3}{4}{acl}
    \depedge[edge unit distance=1em]{4}{6}{obl}
    \depedge[edge unit distance=1em]{6}{5}{case}
    \depedge[edge unit distance=1em]{6}{7}{flat}
	\deproot[edge below]{4}{root}
%	\depedge[edge below, edge unit distance=1em]{3}{1}{amod}
%	\depedge[edge below, edge unit distance=1em]{3}{2}{compound}
	\depedge[edge below, edge unit distance=1em]{4}{3}{nsubj}
%	\depedge[edge below, edge unit distance=1em]{4}{6}{obl}
%	\depedge[edge below, edge unit distance=1em]{6}{5}{case}
%	\depedge[edge below, edge unit distance=1em]{6}{7}{flat}
\end{dependency}
\caption{An example of disagreement when annotating tweets with ellipsis.}\label{fig:disagree}
\end{figure}

We report the inter-annotator agreement between the annotators
in the second stage. The agreement on POS is 96.61\%, the unlabeled
dependency agreement is 88.75\% and the labeled dependency agreement
is 84.31\%. Further analysis shows the major disagreements on POS
involve entity names (30.57\%) and topical hashtags (18.11\%).
Taking the example in Figure \ref{fig:non-syn-toks}, ``Fix you'' can
be understood as a verbal phrase but also as the name of the Coldplay's
single and tagged as proper noun. The disagreements on dependencies
annotation come in several different ways. One of these disagreements
is resulted by the ellipsis as shown in Figure \ref{fig:disagree}.
Due to the absence of auxiliary verb, this tweet can either be treated
as a nominal phrase modified by a clause or a sentence with auxiliary
verb missing.

%\subsubsection{Statistics}
%\yjcomment{this part is not finished}
%Tweebank V2 contains 3550 tweets in total, split into training set with 1639 tweets, development set with 710 tweets and test set with 1201 tweets. 
%The training set contains all the 639 unique tweets in the training set of Tweebank V1 and another 1000 tweets in feb\_jul\_16 corpus.
%The development set contains 210 tweets of Tweebank V1 Dev and another 500 tweets in feb\_jul\_16 corpus.
%The test set contains all the 201 tweets in the test set of Tweebank V1 and another 1000 tweets in feb\_jul\_16 corpus.
%
%We process all the raw tweets of these corpora from scratch, from tokenization and POS tagging to dependency annotation.
%As Tweebank V1 and the POS-tagged Twitter corpus of \newcite{gimpel-EtAl:2011:ACL-HLT2011} used a tweet tokenizer~\cite{ICWSM101540} that do not conform with UD guidelines, as we discussed before, we did not use any data of the intermediate steps from these corpora. The basic statistics of Tweebank V2 is shown in Table~\ref{tab1}.
%
%% tweets, tokens, tokens/tweet, part/tweet, token types.
%\begin{table}[t]
%	\centering
%	\begin{tabular}{l r r r} 
%		\hline
%		& 	Train 		& 	Dev		&	Test\\[0.5ex] \hline
%		tweets 		&	1,639 		&	709		&	1,201\\
%		tokens 		&	24,753		&	11,742	&	19,112\\
%		types 		&	7,579			&	4,165		&	6,228\\
%		parts		 	&	3,025 		&	1,402		&	2,252\\ \hline
%	\end{tabular}
%	\caption{Basic Statistics of Tweebank V2}
%	\label{tab1}
%\end{table}
%
%% tokens and its proportions for the previous language phenomena.
%\subsubsection{Twitter Specific Statistics}\label{stats}
%Following the discussion of the Twitter specific linguistic phenomena, we obtain Table~\ref{tab2}.
%
%
%\begin{table*}[t]
%	\centering
%	\small
%	\begin{tabular}{r | l | l | l | r r r r r} 
%		\hline
%		\multicolumn{4}{l}{}	&	Train		&	Test	&	Dev	&	All	&	Per\\[0.5ex] \hline\hline
%		\multirow{10}{*}{\textit{token}}	&	syntactic						&	\multicolumn{2}{l |}{phrasal abbreviation}				
%		&	 12 		&	12	&	10	&	34	&	0.06\%	\\
%		\cline{2-9}
%		&	\multirow{8}{*}{optionally syntactic}	&	\multirow{2}{*}{RT}					&	syntactic	
%		&	 40 		&	19	&	18	&	77	&	0.14\%	\\
%		&								&									&	non-syntactic
%		&	600  		&	500	&	286	&	1386	&	2.49\%	\\
%		\cline{3-9}
%		&								&	\multirow{2}{*}{hashtag}				&	syntactic
%		&	251  		&	212	&	103	&	566	&	1.02 \%	\\
%		&								&									&	non-syntactic
%		&	 290 		&	246	&	155	&	691	&	1.24\%	\\
%		\cline{3-9}
%		&								&	\multirow{2}{*}{at-mentioned}			&	syntactic
%		&	  659		&	420	&	257	&	1336	&	2.40\%	\\
%		&								&									&	non-syntactic
%		&	  640		&	519	&	311	&	1470	&	2.64\%	\\
%		\cline{3-9}
%		&								&	\multirow{2}{*}{emoticon/emoji}			&	syntactic
%		&	  59		&	31	&	24	&	114	&	2.05\%	\\
%		&								&									&	non-syntactic
%		&	 233		&	164	&	98	&	495	&	0.89\%	\\
%		\cline{2-9}
%		&	non-syntactic 					&	\multicolumn{2}{l |}{truncated}
%		&	  111		&	110	&	50	&	271	&	0.49\%	\\
%		
%		\hline
%		\multirow{3}{*}{\textit{structure}}	& 	\multicolumn{3}{l |}{retweet}
%		&	  596		&	498	&	282	&	1376	&	2.47\%	\\
%		&	\multicolumn{3}{l |}{at-mentioned}
%		&	  485		&	305	&	175	&	965	&	1.74\%	\\
%		\hline
%	\end{tabular}
%	\caption{Twitter Specific Statistics of Tweebank V2}
%	\label{tab2}
%\end{table*}

@@

We present a pipeline system to parse tweets into universal dependency.

\subsection{Tokenizer}
Tokenization, as the initial step of many NLP tasks, is non-trivial for
Twitter domain \cite{ICWSM101540}. Due to the informal nature, tweets
present several cases which are unconventional for traditional
toeknization module, like hashtags, at-mentions and emoticons. Some of
them are even ambiguous without understanding their contexts. For example,
the asterisk (*) in {\it 4*3} works as a symbol of multiplying and
delimiter of tokens {\it 4 * 3}; but for the asterisk (*) in {\it SH*T}
works as a mask for censorship, should not be treated as a delimiter.

Considering the complexity of tweets tokenization, instead of manually
crafting rules, we propose to deal with tweets tokenization with a 
character-level bidirectional LSTM (bi-LSTM) sequence-labeling model.
Our model takes the raw sentence and tag each character in this 
sentence as whether it is the beginning of a word.
